A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-12 paper.tex
merge
local FMPs (in progress)

\subsection*{Classical Supersymmetric Field Theories}

Now consider a classical field theory where the spacetime manifold is $M=\RR^n$, which is moreover translation-invariant. Given the data of a spinorial representation $\Sigma$ equipped with a symmetric pairing $\Gamma\colon\Sym^2(\Sigma)\rightarrow V=\CC^n$, we may construct a super Lie algebra of supertranslations $\fA=\Pi\Sigma\oplus V$ with the only nonvanishing Lie bracket given by $\Gamma$. A supersymmetric classical field theory is then a translation-invariant classical field theory on $\RR^n$ where the translation action is extended to an action of the super Lie algebra $\fA$. In addition, we may consider an $R$-symmetry group $G_R$ which acts on $\Sigma$ preserving $\Gamma$ and the $\so(n)$-action and also compatibly on the classical field theory.

@@

The quantization of gauge theories is notoriously subtle and requires a rich theory of renormalization.  One attractive application of the descriptions of the twists of supersymmetric gauge theories that we provide is to study quantization in a setting where the machinery required for renormalization is much more rigid.

To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}. This theory of renormalization can been used to study field theories with and without supersymmetry. \brian{many citations} In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.

In principle, the existence of local counterterms can be used to analyze the full untwisted supersymmetric gauge theories in a mathematically rigorous way.  In practice, however, our approach to renormalization does not provide any significant advantage over traditional approaches used in QFT.  However, a significant simplification happens at the level of the {\em twisted} supersymmetric Yang-Mills theories that we study in this work. To start with, for some examples (but not all), the twisted theory turns out to be a {\em topological field theory}. The theory of renormalization for topological theories can be handled using configuration spaces \cite{Kontsevich}. \brian{more examples}

In the general setting of this paper, while not every twist results in a topological field theory, it does result in a theory in which some directions of spacetime behave topologically, and the remaining directions behave holomorphically. For a mixed holomorphic-topological translation invariant field theory of this type on $\RR^n \times \CC^d$, this means that at least half of the linearly independent translation invariant vector fields act on the field theory in a BRST exact way.

Inspired by the work of Costello and Li in \cite{BCOV1} and Li in \cite{LiFeynman, LiVertex}, the foundations of renormalization for mixed holomorphic-topological field theories on Euclidean space has been developed in \cite{BWhol}. The key result is that the renormalization for mixed holomorphic-topological theories is extremely well-behaved from an analytic perspective. It is shown in the cited work that to first order in $\hbar$, the renormalization of mixed holomorphic/topological theory is {\em finite}. Furthermore, in \cite{LiVertex}, it is shown that in real dimension two this holds to all orders in $\hbar$.

These results yield a salient approach to mathematically characterizing the one-loop quantization of every twist of supersymmetric Yang-Mills theory. Furthermore, in all examples of theories obtained via twisting occuring in dimensions 8 and lower, not much is lost when asking for the one-loop quantization.  The twisted gauge theories here are all either equivalent to $BF$-type theories, or deformations of such theories by a holomorphic differential operator.  Such theories admit prequantizations (that is, they define families of effective field theories compatible under renormalization group flow), which are exact at one loop; meaning all higher order corrections vanish identically.

From this starting point, the first natural problem would be to verify whether these one-loop exact prequantizations define actual quantizations of the classical twisted field theory.  That is, for each such theory, to compute the one-loop anomalies to the solution of the quantum master equation.  This problem comes in two parts: first, to compute the one-loop anomaly to quantization of the theory on flat space $\RR^n \times \CC^d$, and second -- in the case where we can use a twisting homomorphism to define the twisted theory on certain structured $(n+2d)$-manifolds, to calculate the corresponding one-loop anomaly on curved space (in other words, incorporating the computation of a gravitational anomaly). We plan to return to this question in future work.

@@

\textbf{Dimension 2}
\begin{itemize}
 \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) holomorphic twist.}
 \item \emph{Non-Chiral ($\mc N=(4,4), (8,8)$) topological A twist.}
 \item \emph{Non-Chiral ($\mc N=(4,4), (8,8)$) topological B twist.}
 \item \emph{Chiral $\mc N=(0,N_-)$ holomorphic twist.} 
Twisted $(0,2)$ $\sigma$-models were first studied by Witten in \cite{WittenMirror}, and can be used to obtain the chiral algebra of chiral differential operators \cite{WittenCDO}. 
\end{itemize}

@@

@@

We call $\cE$ the \defterm{space of BV fields}. The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook}) 
\[
\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE) .
\]
This bracket is of cohomological degree $+1$. 
This bracket is a graded version to the so-called Soloviev bracket defined on the $\infty$-jets, as described in Section 4 of \cite{GetzlerBracket}.

We explain how to define the BV bracket in our context.  
First note that there is a linear map
\[
\d_{\mr{dR}} \colon \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
\]
defined as follows. 
A local functional $F \in  \oloc(\cE)$ can be written as an equivalence class of a sum of densities of the form
\[
D_1(-) \cdots D_n(-) \Omega
\]
where $D_i$ is a differential operator $D_i \colon \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
Without loss of generality, suppose $F$ is of this form. 
Then, we can view $F$ as a functional in $\cO(\cE_c)$ by the assignment
\[
\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
\]
where $\phi$ denotes a compactly supported section. 
Define the symmetric multilinear map
\[
\begin{array}{ccccl}
\d_{\mr{dR}} F & \colon & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
\end{array}
\]
Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{\mr{dR}} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
This implies that $\d_{\mr{dR}} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.

The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega \colon E \cong E^! [-1]$ and hence an isomorphism of local functions
\[
\omega \colon {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
\]
We recognize the right hand side as the space of local vector fields placed in a shifted cohomological degree.
In total, we see that a local functional $F$ determines a local vector field by applying this isomorphism to $\d_{\mr{dR}}F$:
\[
X_F := \omega \circ \d_{\mr{dR}} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
\]
This is the Hamiltonian vector field corresponding to $F$. 
Finally, the BV bracket between local functionals $F, G$ is defined by
\[
\{F, G\} = X_F (G) .
\]

@@

\begin{proof}
Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $S_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.  
The desired equivalence $\Phi \colon (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 \colon E \to E_0$. 
The quasi-inverse $\Psi \colon (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
First $\Psi_1(e) = (e, Q_1(e), 0) \in E$.
For $n > 1$, define
\begin{align*}
\Psi_n \colon \sym^n(E_0) &\to E \\
e_1 \otimes \cdots \otimes e_n &\mapsto (0, I_1^n(e_1, \ldots, e_n), 0).
\end{align*}
These $\Psi_n$ manifestly intertwines the pairings $\omega$ and $\omega'$.  
To see that they intertwine the action functionals, we observe that 
\begin{align*}
S(\Psi(e)) &= S(e, S_1(e), 0) \\
&= S_0(e) + \frac 12 \dvol_M \int (S_1(e)^2 - 2 S_1(e)^2) \\
&= S_0(e) - \frac 12 S_1(e)^2 \\
&= S'(e).
\end{align*}
\end{proof}

@@

\begin{proof}
Concretely, we'll write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
The desired equivalence $\Phi \colon (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 \colon E \to E_0$. 
The quasi-inverse $\Psi \colon (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
The linear term is $\Psi_1(e) = (e, I^{(1)}_{\phi}(e),0,0, I^{(1)}_{\psi^*}(e))$, and for $n > 1$ we have 
\[\Psi_n(e_1\otimes \cdots \otimes e_n) = (0, I^{(n)}_{\phi}(e_1, \ldots, e_n), 0, I^{(n)}_{\psi^*}(e_1, \ldots, e_n)).\]

@@

%There is a corollary of this proposition obtained by iterating the procedure. 
%We will only use a single iteration. 
%
%\begin{cor} \label{cor:quad}
%Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
%Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
%\[
%E = E_0 \oplus \bigoplus_{i=1}^2 \left(F \oplus F^! [-1]\right) \oplus \bigoplus_{i=1}^2 \left(F^!  \oplus F[-1] \right)
%\]
%whose sections we denote by $e_0 + \sum_{i=1}^2 (\phi + \phi_i^*) + \sum_{i=1}^2(\psi_i + \psi_i^*)$ according to the above decomposition. 
%The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$.
%Suppose further that the local functional
%\[
%S = S_0 + \int \left(\phi_2\psi^*_1 + (\phi_2 - \phi_1)\psi_2^*\right) -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} -  \sum_{i=1}^2 \int \phi^*_i I_{\phi^*,i} - \sum_{i=1}^2 \int \psi_i I_{\psi,i} 
%\]
%satisfies the classical master equation, where $I_{\phi,i}, I_{\psi^*,i}, I_{\phi^*,i}, I_{\psi,i}$ are polydifferential operators on fields valued in $F^!$, $F$, $F$, $F^!$ respectively, and which are independent of the fields $\phi_i$ and $\psi^*_i$.
%Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E', \omega_0, S')$ where 
%\[
%E' = E_0 \oplus \left(F_{\phi_1} \oplus F^!_{\phi_1^*} [-1]\right) \oplus \left(F^!_{\psi_1^*} \oplus F[-1]_{\psi_1} \right)
%\]
%and
%\[
%S' = S_0 + \int \phi_1 \psi_1^* - S''
%\]
%where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the functional functional $S$.\brian{finish}
%\end{cor}
%\begin{proof}
%%Notice that the collection of fields $(e_0, \phi_1, \phi_1^*, \phi_2, \phi_2^*, \psi_1, \psi_1^*, \psi_2, \psi_2^*)$ have the same shifted Poisson brackets as the collection of fields $(\phi_1, \phi_1^*
%We begin by making the following change of coordinates on the BV fields:
%\begin{align*}
%\Tilde{\phi}_2 & = \phi_2 - \phi_1 \\
%\Tilde{\psi}_2 & = \psi_2 + \psi_1 \\
%%\Tilde{\phi}^*_2 & = \phi^*_2 - \phi^*_1 \\
%%\Tilde{\psi}^*_2 & = \psi^*_2 + \psi^*_1 
%\end{align*}
%with $\phi_1, \psi_1$ left fixed. 
%This change of coordinates is compatible with the $(-1)$-symplectic pairing. 
%Further, in the new coordinates, the action takes the form
%\[
%S = S_0 + \int \Tilde{\phi}_2\Tilde{\psi}^*_2 + \int \phi_1\psi_2^* -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} 
%\]
%\end{proof}

@@

@@

\subsubsection{Generalized Hodge Theory}
Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.  These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model. By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.

@@

>>>>

\subsection*{Supersymmetric Classical Field Theories}

Now consider a classical field theory where the spacetime manifold is $M=\RR^n$ which is moreover translation-invariant. Given the data of a spinorial representation $\Sigma$ equipped with a symmetric pairing $\Gamma\colon\Sym^2(\Sigma)\rightarrow V=\CC^n$, we may construct a super Lie algebra of supertranslations $\fA=\Pi\Sigma\oplus V$ with the only nonvanishing Lie bracket given by $\Gamma$. A supersymmetric classical field theory is then a translation-invariant classical field theory on $\RR^n$ where the translation action is extended to an action of the super Lie algebra $\fA$. In addition, we may consider an $R$-symmetry group $G_R$ which acts on $\Sigma$ preserving $\Gamma$ and the $\so(n)$-action and also compatibly on the classical field theory.

@@

The quantization of gauge theories is notoriously subtle and leads to a rich theory of renormalization.
An attractive application of the descriptions of the twists of supersymmetric gauge theories that we provide is to study quantization.

To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CosRenorm}. 
This theory of renormalization can been used to study field theories with and without supersymmetry. \brian{many citations}
In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.

In principle, the existence of local counterterms can be used to analyze the full untwisted supersymmetric gauge theories in a mathematically rigorous way.
In practice, however, our approach to renormalization does not provide any significant advantage over traditional approaches used in QFT.

A significant simplification happens at the level of {\em twisted} supersymmetric Yang-Mills theories that we study in this work. 
For few examples, but not all, the twisted theory turns out to be a {\em topological field theory}. 
The theory of renormalization for topological theories can be handled using configuration spaces \cite{Kontsevich}. \brian{more examples}

There are drawbacks to the traditional approach to studying TFTs in the context of supersymmetric Yang-Mills theory.
For instance, upon performing a topological twist, when it exists, one can argue that a significant portion of the data of the full supersymmetric field theory is lost.
Furthermore, there are many examples of twists of supersymmetric field theories that are not topological, so the usual methods of TFT do not apply even at the twisted level. 
Perhaps the most fundamental example of this is $10$-dimensional supersymmetric Yang-Mills theory, where no topological twist exists.

We show that while not every twist results in a topological field theory, it does result in a theory in which some directions of spacetime behave topologically, and the remaining directions behave holomorphically. 
For a translation invariant field theory, this means that at least half of the linearly independent translation invariant vector fields act on the field theory in a BRST exact way, but it is possible that more than half of the translation invariant vector fields act trivially in cohomology.

Inspired by the work of Costello and Li in \cite{BCOV1} and Li in \cite{LiVertex, LiFeynman}, the foundations of renormalization for mixed holomorphic / topological field theories on Euclidean space has been developed in \cite{BWhol}.
The key result is that the renormalization for mixed holomorphic / topological theories is extremely well-behaved from an analytic perspective. 
It is shown in the cited work that to first order in $\hbar$, the renormalization of mixed holomorphic/topological theory is {\em finite}. 
Furthermore, in \cite{LiVertex}, it is shown that in real dimension two this holds to all orders in $\hbar$.

These results yield a salient approach to mathematically characterizing the one-loop quantization of every twist of supersymmetric Yang-Mills theory. 
Furthermore, in many examples of theories obtained via twisting not much is lost when asking for the one-loop quantization.
The twisted gauge theories of type $BF$, which are plentiful in the examples we consider,  admit quantizations which are exact at one loop; meaning all higher order corrections vanish identically. 
While ambitious, the first natural problem would be to compute anomalies which we plan to return to in future work.

@@

\textbf{Dimension 2}
\begin{itemize}
 \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) holomorphic twist.}
 \item \emph{Non-Chiral ($\mc N=(4,4), (8,8)$) topological A twist.}
 \item \emph{Non-Chiral ($\mc N=(4,4), (8,8)$) topological B twist.}
 \item \emph{Chiral $\mc N=(0,N_-)$ holomorphic twist.}
\end{itemize}

@@

\subsection*{Applications to Quantization and a Relationship to Factorization algebras}
%\addcontentsline{toc}{subsection}{Applications to quantization and a relationship to factorization algebras}

The quantization of gauge theories is notoriously subtle and leads to a rich theory of renormalization.
An attractive application of the descriptions of the twists of supersymmetric gauge theories that we provide is to study quantization.

To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}. 
In the context of (non-supersymmetric) Yang-Mills theory it is shown that this theory of re

@@

We call $\cE$ the \defterm{space of BV fields}. The pairing $\omega$ equips the algebra of local functionals on $E$ with a \defterm{BV bracket} (see \cite[Chapter 5.3]{CostelloBook}) 
\[
\{-,-\}\colon \oloc(\cE) \times \oloc(\cE) \to \oloc(\cE) .
\]
This bracket is of cohomological degree $+1$. 
We will now explain how to define the BV bracket.  First note that there is a linear map
\[
\d_{\mr{dR}} : \oloc(\cE) \to {\rm Fun}_{\rm loc}(\cE, \cE^!) 
\]
defined as follows. 
A local functional $F \in  \oloc(\cE)$ can be written as an equivalence class of a sum of densities of the form
\[
D_1(-) \cdots D_n(-) \Omega
\]
where $D_i$ is a differential operator $D_i : \cE \to C^\infty_M$ and $\Omega$ is a density on $M$. 
Without loss of generality, suppose $F$ is of this form. 
Then, we can view $F$ as a functional in $\cO(\cE_c)$ by the assignment
\[
\phi \mapsto \int_M D_1(\phi) \cdots D_n(\phi) \Omega
\]
where $\phi$ denotes a compactly supported section. 
Define the symmetric multilinear map
\[
\begin{array}{ccccl}
\d_{\mr{dR}} F & \colon & \cE_c^{\times (n-1)} & \to & \cE^\vee \\
& & (\phi_1, \ldots, \phi_{n-1}) & \mapsto & D_1(\phi_1) \cdots D_{n-1}(\phi_{n-1}) D_{n} (-) + \{{\rm symmetric\;terms}\} .
\end{array}
\]
Integrating by parts, we see that for any $(n-1)$-tuple $\phi_1, \ldots, \phi_{n-1} \in \cE_c$ that the linear functional $(\d_{\mr{dR}} F) (\phi_1,\ldots, \phi_{n-1})$ is an element of $\cE^!$. 
This implies that $\d_{\mr{dR}} F \in {\rm Fun}_{\rm loc}(\cE, \cE^!)$.

The non-degenerate pairing $\omega$ determines a bundle isomorphism $\omega \colon E \cong E^! [-1]$ and hence an isomorphism of local functions
\[
\omega : {\rm Fun}_{\rm loc}(\cE, \cE^!) \cong {\rm Fun}_{\rm loc}(\cE, \cE[1]) .
\]
We recognize the right hand side as the space of local vector fields placed in a shifted cohomological degree.
In total, we see that a local functional $F$ determines a local vector field by applying this isomorphism to $\d_{\mr{dR}}F$:
\[
X_F := \omega \circ \d_{\mr{dR}} (F) \in  {\rm Fun}_{\rm loc}(\cE, \cE[1])  .
\]
This is the Hamiltonian vector field corresponding to $F$. 
Finally, the BV bracket between local functionals $F, G$ is defined by
\[
\{F, G\} = X_F (G) .
\]

@@

\begin{proof}
Concretely, suppose that the linear part of $S_1$ is given by an operator $Q_1$, and the interacting part of $S_1$ is given by a functional $I_1 = \sum_{n=1}^\infty I_1^n$.  
The desired equivalence $\Phi : (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 : E \to E_0$. 
The quasi-inverse $\Psi : (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
First $\Psi_1(e) = (e, Q_1(e), 0) \in E$.
For $n > 1$, define
\begin{align*}
\Psi_n \colon \sym^n(E_0) &\to E \\
e_1 \otimes \cdots \otimes e_n &\mapsto (0, I_1^n(e_1, \ldots, e_n), 0).
\end{align*}
These $\Psi_n$ manifestly intertwines the pairings $\omega$ and $\omega'$.  
To see that they intertwine the action functionals, we observe that 
\begin{align*}
S(\Psi(e)) &= S(e, S_1(e), 0) \\
&= S_0(e) + \frac 12 \dvol_M \int (S_1(e)^2 - 2 S_1(e)^2) \\
&= S_0(e) - \frac 12 S_1(e)^2 \\
&= S'(e).
\end{align*}
\end{proof}

@@

\begin{proof}
Concretely, we'll write $\sum_{n \ge 1} I^{(n)}_\phi$ and $\sum_{n \ge 1} I^{(n)}_{\psi^*}$ for the Taylor expansions of $I_\phi$ and $I_{\psi^*}$ respectively.  
The desired equivalence $\Phi : (E, \omega, S) \to (E_0, \omega_0, S')$ is given by the natural projection $\Phi = \Phi_1 : E \to E_0$. 
The quasi-inverse $\Psi : (E_0, \omega_0, S') \to (E, \omega, S)$ is defined as follows.
The linear term is $\Psi_1(e) = (e, I^{(1)}_{\phi}(e),0,0, I^{(1)}_{\psi^*}(e))$, and for $n > 1$ we have 
\[\Psi_n(e_1\otimes \cdots \otimes e_n) = (0, I^{(n)}_{\phi}(e_1, \ldots, e_n), 0, I^{(n)}_{\psi^*}(e_1, \ldots, e_n)).\]

@@

There is a corollary of this proposition obtained by iterating the procedure. 
We will only use a single iteration.

\begin{cor} \label{cor: quad}
Let $(E_0, \omega_0, S_0)$ be a classical BV theory and $F \to M$ a graded vector bundle.
Consider the theory $(E, \omega, S)$ with underlying graded vector bundle
\[
E = E_0 \oplus \bigoplus_{i=1}^2 \left(F \oplus F^! [-1]\right) \oplus \bigoplus_{i=1}^2 \left(F^!  \oplus F[-1] \right)
\]
whose sections we denote by $e_0 + \sum_{i=1}^2 (\phi + \phi_i^*) + \sum_{i=1}^2(\psi_i + \psi_i^*)$ according to the above decomposition. 
The shifted symplectic form $\omega$ is given by the sum of $\omega_0$ plus the standard degree $+1$ pairings between $F, F^! [-1]$ and $F^!, F[-1]$.
Suppose further that the local functional
\[
S = S_0 + \int \left(\phi_2\psi^*_1 + (\phi_2 - \phi_1)\psi_2^*\right) -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} -  \sum_{i=1}^2 \int \phi^*_i I_{\phi^*,i} - \sum_{i=1}^2 \int \psi_i I_{\psi,i} 
\]
satisfies the classical master equation, where $I_{\phi,i}, I_{\psi^*,i}, I_{\phi^*,i}, I_{\psi,i}$ are polydifferential operators on fields valued in $F^!$, $F$, $F$, $F^!$ respectively, and which are independent of the fields $\phi_i$ and $\psi^*_i$.
Then, the classical BV theory $(E, \omega, S)$ is perturbatively equivalent to the BV theory $(E', \omega_0, S')$ where 
\[
E' = E_0 \oplus \left(F_{\phi_1} \oplus F^!_{\phi_1^*} [-1]\right) \oplus \left(F^!_{\psi_1^*} \oplus F[-1]_{\psi_1} \right)
\]
and
\[
S' = S_0 + \int \phi_1 \psi_1^* - S''
\]
where $S'$ is given by setting $\phi = I_{\psi^*}, \phi^* = 0$ and $\psi^* = I_{\phi}, \psi = 0$ in the functional functional $S$.\brian{finish}
\end{cor}
\begin{proof}
%Notice that the collection of fields $(e_0, \phi_1, \phi_1^*, \phi_2, \phi_2^*, \psi_1, \psi_1^*, \psi_2, \psi_2^*)$ have the same shifted Poisson brackets as the collection of fields $(\phi_1, \phi_1^*
We begin by making the following change of coordinates on the BV fields:
\begin{align*}
\Tilde{\phi}_2 & = \phi_2 - \phi_1 \\
\Tilde{\psi}_2 & = \psi_2 + \psi_1 \\
%\Tilde{\phi}^*_2 & = \phi^*_2 - \phi^*_1 \\
%\Tilde{\psi}^*_2 & = \psi^*_2 + \psi^*_1 
\end{align*}
with $\phi_1, \psi_1$ left fixed. 
This change of coordinates is compatible with the $(-1)$-symplectic pairing. 
Further, in the new coordinates, the action takes the form
\[
S = S_0 + \int \Tilde{\phi}_2\Tilde{\psi}^*_2 + \int \phi_1\psi_2^* -  \sum_{i=1}^2 \int \phi_i I_{\phi,i} - \sum_{i=1}^2 \int \psi_i^* I_{\psi^*,i} 
\]
\end{proof}

@@

It will be convenient for us to represent spaces of fields in classical field theories in terms of mapping spaces. In this section we explain their meaning, while in the rest of the paper it will be just a convenient notation.

Recall that a formal moduli problem is a functor from connective dg Artinian algebras $(R, \mathfrak{m})$ to simplicial sets which satisfies a derived version of Schlessinger's condition. We refer to \cite{DAGX,PridhamFMP,Toen} for more details.

For instance, if $\fg$ is an $L_\infty$ algebra, we have a formal moduli problem $B\fg$ defined by
\[(B\fg)(R, \mathfrak{m})=\mathrm{MC}(\fg\otimes \mathfrak{m}),\]
where $\mathrm{MC}(\fg\otimes \mathfrak{m})$ is the simplicial set of Maurer--Cartan elements. The main result of \cite{DAGX,PridhamFMP} is that the functor $B$ defines an equivalence of $\infty$-categories between $L_\infty$ algebras and formal moduli problems. The inverse functor sends a formal moduli problem $\cM$ to the $L_\infty$-algebra $T_{\cM, \ast}[-1]$, the shifted tangent complex of $\cM$ at the basepoint. This important result will only serve as a motivation.

Let $V$ be a $\fg$-representation. Then we may construct an $L_\infty$ algebra
\[L_{V, \fg}=\fg\oplus V[-1]\]
with the only nontrivial brackets coming from the $L_\infty$ brackets on $\fg$ and the action map of $\fg$ on $V$. We introduce the notation
\[V/\fg:= B L_{V, \fg}.\]

\begin{example}
If $\fg$ is an $L_\infty$ algebra, it has an adjoint representation $\fg$. We define the \defterm{$n$-shifted tangent bundle} of $B\fg$ to be
\[T[n] B\fg = \fg[n+1] / \fg.\]
\label{ex:tangentBg}
\end{example}

\begin{example}
Suppose $\fg$ is an $L_\infty$ algebra which is bounded as a complex and has finite-dimensional graded pieces. Then $\fg^*$ is a coadjoint representation of $\fg$. We define the \defterm{$n$-shifted cotangent bundle} of $B\fg$ to be
\[T^*[n] B\fg = \fg^*[n-1] / \fg.\]
\label{ex:cotangentBg}
\end{example}

\begin{definition}
Let $\fg$ be an $L_\infty$ algebra. A \defterm{$\Gm$-action} on a formal moduli problem $B\fg$ is a weight grading $\fg = \oplus_m \fg(m)$ compatible with the $L_\infty$ structure.
\end{definition}

\begin{example}
Suppose $\fg$ is an $L_\infty$ algebra and $V$ is a $\fg$-representation. Then $V/\fg$ carries a $\Gm$-action: the underlying $L_\infty$ algebra $\fg\oplus V[-1]$ carries a grading where $\fg$ has weight $0$ and $V[-1]$ has weight $1$. For instance, $T[n] B\fg$ and $T^*[n] B\fg$ carry $\Gm$-actions.
\end{example}

Now suppose $L$ is a local $L_\infty$ algebra on a manifold $M$. For every open subset $U\subset M$ we have a formal moduli problem
\[(B L)(U) = B L(U),\]
i.e. $\cL$ defines a presheaf $B L$ of formal moduli problems on $M$. The following definition was introduced in \cite[Definition 4.1.3.3]{Book2}.

\begin{definition}
A \defterm{local formal moduli problem on $M$} is a presheaf of formal moduli problems on $M$ represented by a local $L_\infty$ algebra.
\end{definition}

\begin{remark}
In \cite{Book2} an extra assumption of ellipticity is required for the local $L_\infty$ algebras considered. It is only relevant for quantization which we do not consider in this paper, so we will drop this extra assumption.
\end{remark}

\begin{example}
Let $X,Y$ be complex manifolds, $M$ a smooth manifold and $B\fg$ a formal moduli problem represented by an $L_\infty$ algebra $\fg$. Then we may define the following local formal moduli problem on $X\times Y\times M$. Let $\Omega^{0, \bullet}_X$ be the graded vector bundle of $(0, n)$-forms on $X$, $\Omega^{\bullet, \bullet}_Y$ be the graded vector bundle of $(p, q)$-forms on $Y$ and $\Omega^\bullet_M$ a graded vector bundle of differential forms on $M$. We may then consider a graded vector bundle
\[L = \Omega^{0,\bullet}_X\otimes \Omega^{\bullet, \bullet}_Y\otimes \Omega^\bullet_M\otimes \fg\]
on $X\times Y\times M$. It carries a differential given by the sum $\ol\dd_X + \ol\dd_Y + \d_M + \d_\fg$. It also carries a local $L_\infty$ structure which uses the $L_\infty$ structure on $\fg$ and the wedge product of differential forms. We then define
\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg) := B L.\]
\label{ex:mappingspace}
\end{example}

\begin{remark}
A smooth complex algebraic variety $X$ gives rise to derived stacks $X_{\mathrm{Dol}}$ and $X_{\mathrm{dR}}$ defined by Simpson \cite{Simpson,PTVV}. So, given smooth complex algebraic varieties $X,Y,M$ and a derived stack $F$ we may consider the mapping stack
\[\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, F).\]
Example \ref{ex:mappingspace} is an analogous construction in the world of formal moduli problems.
\end{remark}

\begin{example}
Consider $X, Y, M, \fg$ as in Example \ref{ex:mappingspace} and suppose $E$ is a line bundle on $X\times Y\times M$, equipped with a holomorphic structure along $X\times Y$ and a flat connection along $M$. Moreover, assume $B\fg$ carries a $\Gm$-action. We then have a local $L_\infty$ algebra
\[L = \bigoplus_m \Omega^{0,\bullet}_X\otimes \Omega^{\bullet, \bullet}_Y\otimes \Omega^\bullet_M\otimes \fg(m)\otimes E^{\otimes m}\]
on $X\times Y\times M$. We define
\[\Sect(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg\times_{\Gm} L) := B L.\]
\end{example}

As in Examples \ref{ex:tangentBg} and \ref{ex:cotangentBg}, we may define shifted tangent and cotangent bundles of a local formal moduli problem which give more examples.

\begin{lemma}
Consider $X,Y,M, \fg$ as in Example \ref{ex:mappingspace}. The local formal moduli problem $T^*[n]\map(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, B\fg)$ is isomorphic to the local formal moduli problem
\[\Sect\left(X\times Y_{\mathrm{Dol}}\times M_{\mathrm{dR}}, T^*[n+\dim(X)+2\dim(Y)+\dim(M)] B\fg\times_{\Gm} (K_X\otimes \Dens_M)\right),\]
where $K_X$ is the canonical bundle of $X$ and $\Dens_M$ is the line bundle of densities on $M$.
\end{lemma}
\begin{proof}
The claim follows from the following isomorphisms of graded vector bundles:
\begin{align*}
\left(\Omega^{0, \bullet}_X\right)^!&\cong \Omega^{0, \bullet}_X\otimes K_X[\dim(X)] \\
\left(\Omega^{\bullet, \bullet}_Y\right)^!&\cong \Omega^{\bullet, \bullet}_Y[2\dim(Y)] \\
\left(\Omega^\bullet_M\right)^!&\cong \Omega^\bullet_M\otimes \Dens_M[\dim(M)].
\end{align*}
\end{proof}

Given a local formal moduli problem, we may talk about shifted symplectic structures \cite{PTVV} on it. In this paper will only be interested in a strict notion as follows.

\begin{definition}
Let $\cM$ be a local formal moduli problem on $M$ represented by a local $L_\infty$ algebra $L$. A \defterm{strict $n$-shifted symplectic structure} on $\cM$ is a pairing $\omega\colon L\otimes L\rightarrow \Dens_M[n-2]$ satisfying the following conditions:
\begin{enumerate}
\item It is fiberwise nondegenerate.

\item It is graded skew symmetric.

\item The pairing
\begin{align*}
\cL_c\otimes \cL_c&\rightarrow \CC \\
\alpha\otimes \beta&\mapsto \int_M \langle \alpha, \beta\rangle
\end{align*}
is an invariant pairing on the $L_\infty$ algebra $\cL_c$.
\end{enumerate}
\end{definition}

\begin{definition}
A \defterm{classical BV field theory} (or, simply, classical field theory) is a local formal moduli problem on the spacetime manifold $M$ equipped with a strict $(-1)$-shifted symplectic structure.
\end{definition}

@@

\subsubsection{Generalized Hodge Theory}
Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.  These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}. By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.

@@

\brian{Should we also compute what happens to the $(0,2)$ Fermi multiplet?}
